Cloud correction and filtering of operational microwave humidity radiances with case specific uncertainty estimation

### 2020-09-18 Article/ici_submm_cloudcorr.tex
Removed temporary outline of sections.

The approach is demonstrated on a combination of 183\,GHz channels (following
\citet{buehler:aclou:07}), but we mainly explore the cloud correction (of
183\,GHz data) that will be possible when sub-millimetre data will be at hand
in some years. This wavelength region will be introduced by the Ice Cloud
Imager (ICI, \citet{eriksson:towar:20}), but likely also be included in several
smaller missions (such as AWS presented below). The focus on ICI is motivated
by several reasons. The true potentail of the QRNN cloud correction approach is
likely not revealed if tested on existing data and applying ICI data for cloud
filtering has not earlier been discussed. It is also argued that the cloud
correction makes it possible to make good use of ICI data already in clear-sky
assimilation, a fact that should speed up the use of this novel data source.

@@

\section{Outlook and Conclusions}  %% \conclusions[modified heading if necessary]

\newpage

\section*{Outline of sectioning}

2 Data and methods

2.1 Satellite sensors

2.1.1 Ice Cloud Imager (ICI)

2.1.2 Microwave Imager (MWI)

2.1.3 Arctic Weather Satellite (AWS)

2.2 Quantile Regression Neural Network (QRNN)

2.2.1 Theory

2.2.2 Evaluation metrics

2.3 Simulations

2.3.1 Input data

2.3.2 Simulation setup

2.3.3 Produced dataset
(If diifers between ICI, MWI and AWS, clarify this)

\noindent 3 Results

Short recap of aim of correction. We also use the correction as a filter, using
a threshold on the correction. We use 5K (?) threshold as example.

3.1 QRNN network configurations and training

3.2 ICI

3.2.1 Example results

Show a few estimated posterior distributions (one figure) and distribution of
predicted values (Fig 2)

3.2.2 Error of best estimate

3.2.3 Predicted uncertainty

3.3 MWI

3.3.1 MWI alone

Just 183 GHz channels, original noise

3.3.2 MWI and ICI

As in present version

3.4 AWS

\noindent 4 Discussion

\noindent 5 Conclusion

\newpage

>>>>

The approach is demonstrated on a combination of 183\,GHz channels (following
\citet{buehler:aclou:07}), but we mainly explore the cloud correction (of
183\,GHz data) that will be possible when sub-millimetre data will be at hand
in some years. This wavelength region will be introduced by the Ice Cloud
Imager (ICI, \citet{eriksson:towar:20}), but likely also be included in several
smaller missions (such as AWS, presented below). \todo{Explain what sub-mm can
  do}.}

The focus on ICI is motivated by several reasons. The true potentail of the
QRNN cloud correction approach is likely not revealed if tested on existing
data and applying ICI data for cloud filtering has not earlier been discussed.
It is also argued that the cloud correction makes it possible to make good use
of ICI data already in clear-sky assimilation, a fact that should speed up the
use of this novel data source.

@@

\section{Conclusion and outlook}  %% \conclusions[modified heading if necessary]
%
To be written \dots
